Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-26 manuscript/manuscript.Rmd
reward shaping, normalizing, hyperparameter tuning

\textbf{Training a DRL agent.}
We trained a DRL agent parametrized by a neural network $\theta$ with two hidden, 64-neuron, layers.
The state space used was a cube $[0,2]^{\times 3}$, while the policies explored mapped states $N_t$ to a single number, $h_t = \pi_\theta(N_t)$, the harvest quota on species $X$ at that timestep.
Each episode in the training and in the evaluation stages was at most 600 time steps long.
Episodes were ended early in case of a ‘‘near-extinction event,’’ a moment in which any of the populations dipped below a threshold value, i.e.,
\begin{align}
  \label{eq:thresh}
  X_t \leq X_{\text{thresh.}},\quad
  Y_t \leq Y_{\text{thresh.}},\quad
  \text{or,}\quad
  Z \leq Z_{\text{thresh.}}.
\end{align}
The reward function had two componenets:
First, at each time step the harvest $h_t$ was received as a reward.
Second, if the episode ended early (say, at time-step $t$) because of a near-extinction event, a negative reward of $-50/t$ was awarded.
The constant 50 was chosen so as to select against highly extractive policies in the early stages of training, and thus guide the agent towards sustainable policies.

>>>>

\textbf{Training a DRL agent.}
We trained a DRL agent parametrized by a neural network $\theta$ with two hidden, 64-neuron, layers.
The state space used was a cube $[0,2]^{\times 3}$, while the policies explored mapped states $N_t$ to a single number, $h_t = \pi_\theta(N_t)$, the harvest quota on species $X$ at that timestep.
Each episode in the training and in the evaluation stages was at most 600 time steps long.
Episodes were ended early in case of a ‘‘near-extinction event,’’ a moment in which any of the populations dipped below a threshold value, i.e.,
\begin{align}
  \label{eq:thresh}
  X_t \leq X_{\text{thresh.}},\quad
  Y_t \leq Y_{\text{thresh.}},\quad
  \text{or,}\quad
  Z \leq Z_{\text{thresh.}}.
\end{align}
The reward function had two componenets:
First, at each time step the harvest $h_t$ was received as a reward.
Second, if the episode ended early (say, at time-step $t$) because of a near-extinction event, a negative reward of $-50/t$ was awarded.
The constant 50 was chosen so as to select against highly extractive policies in the early stages of training, and thus guide the agent towards sustainable policies.
This technique, falling under the ‘‘umbrella’’ category of *reward shaping*, is commonly used -- alongside hyper-parameter tuning and state space normalization -- to improve the speed of training by avoiding badly-performing local optima in the gradient ascent algorithm.

Thus, we normalized state space (to be contained in a cube of length 2) and engaged in reward shaping in order to optimize our agent's learning.
We did not need to tune hyper-parameters for this goal, however.
